--- 
title: "607:  Assignment 5"
author: "Nilsa Bermudez"
date: "2/28/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: zenburn
--- 


library(tidyr)
library(dplyr)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The chart above describes arrival delays for two airlines across five destinations. Your task is to:

(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above.
You’re encouraged to use a “wide” structure similar to how the information appears above, so
that you can practice tidying and transformations as described below.

(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy
and transform your data.
(3) Perform analysis to compare the arrival delays for the two airlines.

(4) Your code should be in an R Markdown file, posted to rpubs.com, and should include narrative
descriptions of your data cleanup work, analysis, and conclusions. Please include in your
homework submission:

The URL to the .Rmd file in your GitHub repository. and the URL for your rpubs.com web page

## 1. Load the flights csv file

```{r LoadFlights}
flights <- read.table("https://raw.githubusercontent.com/nilsabermudez/607/master/flights.csv", header=TRUE, sep=",")

```

## 2. Perform some data cleansing: Remove blank line - line 3

```{r}

flights <- flights[-c(3),]
head(flights)
```


## 3.  Cleanup the column names - rename columns

```{r}
names(flights) <- c("Airline", "Status", "LosAngeles", "Phoenix", "SanDiego", "SanFrancisco", "Seattle")
flights
```


## 4.  Add airline names to "" row 

```{r} 
flights$Airline<-as.character(flights$Airline)
flights$Airline[flights$Airline==""]<-c("ALASKA","AM WEST")

head(flights)
```

## 5.  Use tidyr to gather the data

```{r}
flightdata <- tidyr::gather(flights, "City", "NumberOfFlights", 3:7)

flightdata
```

## 6.  Gather and spread the data

```{r}

flightdata <- dplyr::tbl_df(flights)
flightdata <- tidyr::gather(flights, "City", "NumberOfFlights", 3:7)
flightdata <- tidyr::spread(flightdata, Status, NumberOfFlights)
flightdata
```

## 7.  More data cleansing

```{r}
names(flightdata) <- c("Airline", "City","Delayed","OnTime")

flightdata$OnTime <- gsub(',', '',flightdata$OnTime)
flightdata$OnTime <- as.numeric(as.character(flightdata$OnTime))
flightdata$Delayed <- as.numeric(as.character(flightdata$Delayed))
flightdata <- dplyr::mutate(flightdata,Total = Delayed / OnTime)
flightdata

```

## Conclusion

AM West has the highest delays for all Cities.  AM West also had more flights, so more flights for this airline, means a higher # of delays.



