---
title: "Assignment 10"
author: "Nilsa Bermudez"
date: "4/4/2020"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: cosmo
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE)

```


```{r}
Sys.setenv(R_GSCMD="C:/Program Files/gs/gs9.05/bin/gswin32c.exe")
#install.packages('extrafont')
library(extrafont)
library(wordcloud)
suppressMessages(library(ggplot2));
suppressMessages(library(textdata));
suppressMessages(library(lexicon));
suppressMessages(library(DT));
suppressMessages(library(tidytext));
suppressMessages(library(jsonlite));
suppressMessages(library(readr));
suppressMessages(library(dplyr));
suppressMessages(library(stringr));
```


## Introduction 

In Text Mining with R, Chapter 2 looks at Sentiment Analysis.  In this assignment, I'll start by getting the primary example code from chapter 2 - Jane Austen 2.2 Sentiment analysis with inner join and word cloud.  

I've chosen Yelp reviews as my corpus. 

```{r} 
warning=FALSE
```

```{r, echo=FALSE}
1 + 1
```

```{r}
# Load library
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidytext)
library(tidyr)
library(ggplot2)
library(textdata)
library(wordcloud)

# get linenumber and chapter 
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)


nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
library(ggplot2)

library(janeaustenr)
library(dplyr)
library(stringr)

original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

original_books
library(tidytext)
tidy_books <- original_books %>%
  unnest_tokens(word, text)

tidy_books

data(stop_words)

tidy_books <- tidy_books %>%
  anti_join(stop_words)


tidy_books %>%
  count(word, sort = TRUE) 

```



# Here we have Jane Austen's Graph of most used words:
```{r JaneGraph}
tidy_books %>%
  count(word, sort = TRUE) %>%
  filter(n > 600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

```

# Here we have Jane Austen's wordcloud:

```{r JaneWordCloud}

tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100,scale=c(2,1.0),))

```


```{r ReadFile}

rs <- read.csv("https://raw.githubusercontent.com/nilsabermudez/607/master/yelp.csv", header=TRUE, sep=",")

```


```{r}
 #rs %>%  select(1,3,4,5)


```


```{r SplitTheDataRenameColumn}
splitrs <- splitstackshape::cSplit(rs, "text", " ", "long")
colnames(splitrs)[5] <- "word"

```

```{r GetSentiments}
bing <- get_sentiments("bing");

bing_positive <- get_sentiments("bing") %>% 
  filter(sentiment == "positive")
#bing_positive

bing_negative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")
#bing_negative

  ss_positive <- splitrs %>%
     inner_join(bing_positive, by = "word")

  ss_negative <- splitrs %>%
     inner_join(bing_negative, by = "word")
  # ss_negative
  # ss_positive

```



```{r GetCountsJustCause}
review_words_counted_positive <-  count(ss_positive, c('word'))
review_words_counted_negative <-  count(ss_negative, c('word'))

 review_words_counted_negative
 review_words_counted_positive
 
 
  review_words_counted <- splitrs %>%
   count(review_id, business_id, stars, word) %>%
   ungroup()
  review_words_counted
  
  #GetalltheSentiments
  bing_word_counts <- splitrs %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
  
   bing_word_counts
```


# Here we have Yelp's top 10 most used words in their reviews:

```{r Top10InGraph}

G <- bing_word_counts %>%
   group_by(sentiment=="positive")
top10 <- head(dplyr::arrange(G,desc(n)), n = 10)

  ggplot2::ggplot(data=top10, ggplot2::aes(x=reorder(word, -n), y=n)) +
  ggplot2::geom_bar(stat="identity",fill='steel blue') +
  ggplot2::labs(x="Top Words",y="Frequency") +
  ggplot2::ggtitle("Top 10 Positive Words in Yelp Reviews") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, vjust = 0.5, hjust=1))    


```



# Here we have Yelp's word cloud of reviews:

```{r GetWordCloud}
top50 <- head(dplyr::arrange(G,desc(n)), n = 50)

top50 %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100,rot.per=0.25,scale=c(2,1.0)))


```

