---
title: "Assignment_9"
author: "Nilsa Bermudez"
date: "3/26/2020"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: zenburn
---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The assignment:
The New York Times web site provides a rich set of APIs, as described here:  https://developer.nytimes.com/apis You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame. 
 

## 1. Registered for my api key



## 2. Set up the URL

We need to insert the API key in order to access the New York Times API. We simply add it onto the end of the URL by using the paste() command.

```{r}
library(DT);
library(jsonlite);
```

```{r URLwithAPIkey}
url <- "https://api.nytimes.com/svc/mostpopular/v2/viewed/1.json"

apikey <- "?api-key=5EYgu00gNdMPkxRf1TuR5AkhKUvr7DOd"
url <- paste(url, apikey, sep="")
x <-fromJSON(url)
names(x)

```


## 3. Viewing the data(no surprise that the last viewable articles are all about the pandemic), we see that the data came out in a dataframe table:


```{r DataFrame}

df <- jsonlite::fromJSON(url, flatten = TRUE)
DT::datatable(x$results)
head(df)

```
