---
title: "Final Project"
author: "Nilsa Bermudez"
date: "5/6/2020"
output: 
  html_document:
    theme: cerulean   
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

```{r load_libraries, results='hide', message=FALSE, warning=FALSE}
library(kableExtra)
suppressMessages(library(plotly))
library(dplyr)
library(DT)
library(stringr)
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
library(tidytext)
library(tidyr)
library(xlsx)
library(reshape2)
#library(usmap)
#library(maps)


```

## Introduction - What is the prevalence of diabetec amputations in the U.S.?

For this project, I will:  
1. Map out the number of amputations for diabetetics by state  
2. Determine what state has the highest # of amputations and which gender is it predominately for.  
3. Determine if across the U.S. if amputations are a predominately higher for a specific gender.  

## 1. The Data

Initially, I wanted to do an analysis on diabetic amputations and socioeconomic factors.  However, I was unable to obtain a large portion of the data due to HIPAA laws.  I then turned to the basic question of - what is the prevalence of diabetes in the U.S.? In doing so, I found some alarming information regarding occurrences of diabetic amputations by gender.

## 2. Get the data and load it into a dataframe

```{r ReadFile}


diabetes <-read.csv("https://raw.githubusercontent.com/nilsabermudez/607/master/complications_hospitalizations_99.csv",   header=TRUE, sep=",")

```


## 3. Subset the Data by extracting the columns needed for this project.

```{r}
CaData <-  diabetes[c(2,3,4,6,26)]
#CaData
CaData2 <-subset(CaData,age==0)
CaData3 <-subset(CaData2,sex==0)
#CaData3

```
## 4. Cleanse the data - remove N/A's

```{r}
Completerecords <- na.omit(CaData3)
#Completerecords
```







```{r Gold }
p <- ggplot2::ggplot(data=Completerecords,  aes(x=state, y=lea_count, color = year,group=year)) +
 
   geom_line(show.legend=TRUE) +   
 theme(legend.position = "top") +
 
  ggplot2::labs(x="States",y="Number of Amputations") +  ggtitle("Amputations across the U.S. due to Diabetes")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, vjust = 0.35, hjust=.5))   


plotly::ggplotly(p,colors = 'YlOrRd' )

```

## 5. Here we see that in 2014, Texas had the most amputations at an alarming number of 11,488 cases.







## 6. Let's drill down and see what the gender distribution was for that year and that state:

```{r}

Texas <- subset(CaData, state=="TEXAS", select = c("state","year", "sex", "age","lea_count"))
TexasMF <- subset(Texas, state=="TEXAS", select = c("state","year", "sex", "age","lea_count"))


```

```{r}

Texas <- Texas[Texas$sex %in% c(1, 2),]
Texas <- subset(Texas, age==0, select = c("state","year", "sex", "age","lea_count"))

p<-ggplot(data=Texas, aes(y=lea_count, x=factor(sex))) +
  geom_bar(stat="identity", width=0.7, fill="steelblue",show.legend=TRUE)+
 theme(legend.position = "top") +
    ggplot2::labs(x="Amputations by Gender",y="Number of Amputations") +  ggtitle("2014 - State of Texas Amputations by Gender")+ 
   scale_x_discrete(labels=c("1" = "Males", "2" = "Females")) 

 p + guides(color = guide_legend(reverse = TRUE))
```
 
 
## 7. Let's map out the U.S. Amputations by Gender for the 2014 year
 
```{r}
AllData <- subset(CaData, age==0, select = c("state","year", "sex", "age","lea_count"))

USAmputations <-subset(AllData, year==2014, select = c("state","year", "sex", "age","lea_count"))
USAmputations <-  USAmputations[USAmputations$sex %in% c(1, 2),]
#USAmputations

```

```{r}


p <- ggplot2::ggplot(data=USAmputations,  aes(x=state, y=lea_count, group=state, fill= sex, color=sex))  +geom_bar(stat = "identity", position = "dodge", width=.5)+theme(legend.position = "none") +
   scale_x_discrete(labels=c("1" = "Males", "2" = "Females")) +
  ggplot2::labs(x="States",y="Number of Amputations") +  ggtitle("Amputations across the U.S. due to Diabetes by Gender - 2014")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, vjust = 0.35, hjust=.5)) +
  theme(panel.grid.major.x = element_blank()) 

 ggplotly(tooltip = c("text", "x", "fill", "y")) 
 
 
```


## 8. Looking at the Poverty estimate for the state of Texas, it is over 4 million.  

```{r}
CensusPoverty <-read.csv("https://raw.githubusercontent.com/nilsabermudez/607/master/est14us.csv",skip=5,  header=TRUE, sep=",")
CensusPoverty <- subset(CensusPoverty,  select = c(Postal.Code, Poverty.Estimate..All.Ages))
datatable(CensusPoverty, options = list(pageLength = 5))

```




## Conclusions

In this project:

1. In 2014, Texas had the highest number of amputations.
2. Males are getting amputations at a higher rate than females not only in Texas in 2014 - but across the U.S. in general.
3. Socioeconomic challenges may be a factor for the high number of amputees in Texas.

This analysis could be presented to the diabetic community as a teaching example of the dangerous complications due to having diabetes.  


References:  

https://www.census.gov/data/datasets/2014/demo/saipe/2014-state-and-county.html  
https://nccd.cdc.gov/CKD/default.aspx  
