---
title: "Project_2_Part_3"
author: "Nilsa Bermudez"
date: "3/7/2020"
output: html_document
---

library(sqldf)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction

(1) Choose any three of the “wide” datasets identified in the Week 6 Discussion items. (You may
use your own dataset; please don’t use my Sample Post dataset, since that was used in your
Week 6 assignment!) For each of the three chosen datasets:
 Create a .CSV file (or optionally, a MySQL database!) that includes all of the information
included in the dataset. You’re encouraged to use a “wide” structure similar to how the
information appears in the discussion item, so that you can practice tidying and
transformations as described below.
 Read the information from your .CSV file into R, and use tidyr and dplyr as needed to
tidy and transform your data. [Most of your grade will be based on this step!]
 Perform the analysis requested in the discussion item.
 Your code should be in an R Markdown file, posted to rpubs.com, and should include
narrative descriptions of your data cleanup work, analysis, and conclusions.
(2) Please include in your homework submission, for each of the three chosen datasets:
 The URL to the .Rmd file in your GitHub repository, and
 The URL for your rpubs.com web pag



## Read the file - Add column names
```{r readFile}

training <- read.table("https://raw.githubusercontent.com/nilsabermudez/607/master/adult-training.csv", header=FALSE, sep=",")


head(training)

 names(training) <- c("age", "Employed","Number", "Education","YearsOfSchool","MaritalStatus","Profession","Relation","Race","Gender","CapitalGain","CapitalLoss","HoursPerWeek","BirthPlace","Salary")
 
head(training)


```
## 


```{r}
 
Data <- sqldf::sqldf("select age, MaritalStatus, Gender, HoursPerWeek, Salary from training") 
  
#print(Data)
 
```


# How many Males over 40 are not married and work over 40 hours a week


```{r}
 
Data <- sqldf::sqldf("select count(*) from training where age >40 and HoursPerWeek >40 and MaritalStatus <> 'Married-civ-spouse'") 
  
print(Data)
 
```



# How many Males over 40 are married and work over 40 hours a week


```{r}
 
Data <- sqldf::sqldf("select count(*) from training where age >40 and HoursPerWeek >40 and MaritalStatus ='Married-civ-spouse'") 
  
print(Data)
 
 
```


## Conclusion
It appears that Males over 40 who are married tend not to work over 40 hours a week.

