---
title: "Project 2 - Part 2"
author: "Nilsa Bermudez"
date: "3/8/2020"
output: html_document
---





library(sqldf)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction

(1) Choose any three of the “wide” datasets identified in the Week 6 Discussion items. (You may
use your own dataset; please don’t use my Sample Post dataset, since that was used in your
Week 6 assignment!) For each of the three chosen datasets:
 Create a .CSV file (or optionally, a MySQL database!) that includes all of the information
included in the dataset. You’re encouraged to use a “wide” structure similar to how the
information appears in the discussion item, so that you can practice tidying and
transformations as described below.
 Read the information from your .CSV file into R, and use tidyr and dplyr as needed to
tidy and transform your data. [Most of your grade will be based on this step!]
 Perform the analysis requested in the discussion item.
 Your code should be in an R Markdown file, posted to rpubs.com, and should include
narrative descriptions of your data cleanup work, analysis, and conclusions.
(2) Please include in your homework submission, for each of the three chosen datasets:
 The URL to the .Rmd file in your GitHub repository, and
 The URL for your rpubs.com web pag



## Read the file - Clean up column names
```{r readFile}

diabetes =read.table("https://raw.githubusercontent.com/nilsabermudez/607/master/diabetes.csv", header=TRUE, sep=",")

head(diabetes)

names(diabetes) <- c("Pregnancies","Glucose","BloodPressure","SkinThickness","Insulin","BMI","DiabetesPedigreeFunction","Age","Outcome")

head(diabetes)
```

## Does a higher number of pregnancies predict diabetes?  



```{r}
HighPreg <- sqldf::sqldf("select count(Pregnancies) from diabetes where Pregnancies >=3")
TotalPreg <- sqldf::sqldf("select count(*) from diabetes")

HighPreg
TotalPreg
Percentage <-HighPreg/TotalPreg
Percentage

```




## Does a higher age predict diabetes?
```{r}
HighAge <- sqldf::sqldf("select count(Age) from diabetes where Age >=40")
TotalAge <- sqldf::sqldf("select count(*) from diabetes")

HighAge
TotalAge
Percentage <-HighAge/TotalAge
Percentage
```


##  There are a lot of factors that increase your chance for diabetes.  Having a higher # of pregnancies and being in an older age bracket definitely increase your chances.

